### 2015-03-20 paper_10_intro.tex
updates through chapter 4
make testcase one word

    This dissertation 
    provides a technique for a Software Development Organization (SDO)
    \nomenclature{SDO}{Software Development Organization}to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 key result indicators
    of an SDO: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.  The single
    number is targeted for upper-level management whom need a quick
    and simple strategy to evaluate the performance of the organization.

@@

    SDOs need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    \nomenclature{CRI}{Cumulative Result Indicator}
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus solely on the source code
    being produced.  However, an SDO does more
    than just produce source code.  There is documentation to be
    written, test cases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall SDO, not just the
    source code.

@@

\subsection{TERMINOLOGY}
    Like any other business domain, the software engineering field has number
    of specific terms.  Many of these terms will be used throughout the remainder
    of the document, so definitions are provided.

@@

        \item[Application] - a software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release 
        \item[SIT] (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
            \nomenclature{SIT}{Systems Integration Testing} 
        \item[UAT] (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occurred for
            UAT, the software system is ready to proceed to production
            \nomenclature{UAT}{User Acceptance Testing} 
        \item[PROD] (Production) - The software has been released to the 
        final audience. \nomenclature{PROD}{Production} 
        \item[defect] ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed test cases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

@@

    CMMI-Dev is a modification of the CMMI specific to the 
    development activities applied to products
    and services.  The practices covered in 
    CMMI-Dev include project management, 
    systems engineering, hardware engineering, process 
    management, software engineering, and 
    other maintenance processes.  Five maturity levels are 
    specified, and they include the 
    existence of a number of process areas.  The 5 maturity 
    levels and the process areas are specified as follows.

>>>>

    This dissertation 
    provides a technique for a Software Development Organization (SDO)
    \nomenclature{SDO}{Software Development Organization} to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 key result indicators
    of an SDO: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.  The single
    number is targeted for upper-level management who need a quick
    and simple strategy to evaluate the performance of the organization.

@@

    SDOs need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    \nomenclature{CRI}{Cumulative Result Indicator}
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus solely on the source code
    being produced.  However, an SDO does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall SDO, not just the
    source code.

@@

\subsection{TERMINOLOGY}
    Like any other business domain, the software engineering field has a number
    of specific terms.  Many of these terms will be used throughout the remainder
    of the document, so definitions are provided.

@@

        \item[Application] - a software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release 
        \item[SIT] (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
            \nomenclature{SIT}{Systems Integration Testing} 
        \item[UAT] (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occurred for
            UAT, the software system is ready to proceed to production
            \nomenclature{UAT}{User Acceptance Testing} 
        \item[PROD] (Production) - The software has been released to the 
        final audience. \nomenclature{PROD}{Production} 
        \item[defect] ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed testcases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

@@

    CMMI-Dev is a modification of the CMMI specific to the 
    development activities applied to products
    and services.  The practices covered in 
    CMMI-Dev include project management, 
    systems engineering, hardware engineering, process 
    management, software engineering, and 
    other maintenance processes.  Five maturity levels are 
    specified, and they include the 
    existence of a number of process areas.  The five maturity 
    levels and the process areas are specified as follows.

### 2015-03-20 paper_40_cri.tex
some more modifications and include CRI element scatterplot matrix
make testcase one word

                The development and testing effort can come from any of 
                the following choices for effort. It is possible
                that other measures will work for effort.
                \begin{description}
                    \item[Actual Time] This number is a representation of the 
                        total amount of time spent on a project.  This number
                        can be measured in any unit of time: hours, days, weeks,
                        etc.  Actual time can be applied to development or testing
                        effort.
                    \item[Estimated Time] This number is a representation of the 
                        initial estimated amount of time spent on a project.  This number
                        can be measured in any unit of time: hours, days, weeks,
                        etc.  Estimated time can be applied to development or testing
                        effort.  It is common for the estimated and actual times
                        to be different.
                    \item[SLOC]  This number is the count of 
                        the total number of lines of source code for a project. 
                        Obviously, 
                        this item only counts as a level of
                        effort for development unless coding in used to generate
                        automated test cases. \footnote{Automated testing is the
                        process of creating software to automatically run tests
                        against other software.  The adoption of automated testing
                        is varied and it is not a solution in all cases 
                        \cite{Ramler2006}. }
                    \item[Modified Lines Of Code] This number is a count of the number 
                        of modified lines of source code. Modified lines is 
                        defined as the number of deleted, added, and modified 
                        lines of source code.  This number is different from above
                        since it does not include all the lines of source code.  Similar
                        to above, this number makes more sense for development effort.
                    \item[Test Cases] A test case is a step or series of steps followed
                        to validate some expected outcome of software.  Organizations
                        will create a number of test cases to be validated for a
                        software system.  The number of such test cases could
                        be used as a level of testing effort.
                \end{description}

@@

                The preferred method:
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Scheduled Downtime + Unscheduled Downtime}}
                \]
                and the alternative method:
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Unscheduled Downtime}}
                \]
                The only difference is the removal of scheduled downtime from 
                the calculation.  The calculation approach is typically specified in
                the contract associated with the SLA.  Thus, the Percent Uptime is important
                and it can either be supplied in the data or calculated from the 
                optional fields.

>>>>

                The development and testing effort can come from any of 
                the following choices for effort. It is possible
                that other measures will work for effort.
                \begin{description}
                    \item[Actual Time] This number is a representation of the 
                        total amount of time spent on a project.  This number
                        can be measured in any unit of time: hours, days, weeks,
                        etc.  Actual time can be applied to development or testing
                        effort.
                    \item[Estimated Time] This number is a representation of the 
                        initial estimated amount of time spent on a project.  This number
                        can be measured in any unit of time: hours, days, weeks,
                        etc.  Estimated time can be applied to development or testing
                        effort.  It is common for the estimated and actual times
                        to be different.
                    \item[SLOC]  This number is the count of 
                        the total number of lines of source code for a project. 
                        Obviously, 
                        this item only counts as a level of
                        effort for development unless coding in used to generate
                        automated testcases. \footnote{Automated testing is the
                        process of creating software to automatically run tests
                        against other software.  The adoption of automated testing
                        is varied and it is not a solution in all cases 
                        \cite{Ramler2006}. }
                    \item[Modified Lines Of Code] This number is a count of the number 
                        of modified lines of source code. Modified lines is 
                        defined as the number of deleted, added, and modified 
                        lines of source code.  This number is different from above
                        since it does not include all the lines of source code.  Similar
                        to above, this number makes more sense for development effort.
                    \item[Testcases] A testcase is a step or series of steps followed
                        to validate some expected outcome of software.  Organizations
                        will create a number of testcases to be validated for a
                        software system.  The number of such testcases could
                        be used as a level of testing effort.
                \end{description}

@@

                The preferred method:
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Scheduled Downtime + Unscheduled Downtime}}
                \]
                and the alternative method:
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Unscheduled Downtime}}
                \]
                The only difference is the removal of scheduled downtime from 
                the calculation.  The calculation approach is typically specified in
                the contract associated with the SLA.  Thus, the Percent Uptime is important
                and it can either be supplied in the data or calculated from the 
                optional fields. For the purposes of this dissertation, the percent
                uptime should be handled in decimal form and not as a percent out of 100.
